% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[scale=0.87]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Xuannan} % Your first name
\familyname{Dong} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Resume}
\address{mailbox 5524, 4007 Miramar St.}{La Jolla, CA}
\mobile{(+1) (619) 310-3691}
\email{x3dong@ucsd.edu}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

\vspace{-0.3in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\cventry{09/2021--06/2023}{M.S. in Computer Science}{University California, San Diego}{La Jolla, CA, U.S}{}{}

\cventry{08/2016--07/2020}{B.S. in Electronic Engineering(Automation) and Artificial Intelligence}{University of Science and Technology of China (USTC)}
{Hefei, Anhui, China}{}{3.61/4.3, 86.16/100. Ranking:30/140. \newline 
\cvitem{2019, 2018, 2017}{The First Prize Scholarship, School of Information Technology  (TOP 6\%)}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publication}

\begin{enumerate}
	\item Bang An, \textbf{Xuannan Dong}, Changyou Chen, \emph{Repulsive Bayesian Sampling for Diversified Attention Modeling}, NeurIPS Workshop on Bayesian Deep Learning, 2019.
\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiences} 

\cventry{01/2022--03/2022}{Distributed File Storage System}{Course Project}{University of California, San Diego}{}{}{}
\begin{itemize}
\item[*]{Developed a networked file storage application that is based on Dropbox with \textbf{Golang}, users are allowed to sync files to and from the "cloud". Multiple clients can concurrently connect to the  service to access a common, shared set of files via \textbf{gRPC}.}
\item[*]{Implemented the application to function as a fault tolerant system based on the with \textbf{RAFT protocol}, which allow a collection of machines to work as a coherent group that can survive the failures of some of its members.}
\end{itemize}

\cventry{02/2021--09/2021}{Software Development Intern(Intel)}{Internship}{}{}{}{}
\begin{itemize}
\item[$\bullet$] \textbf{SpeechUI App}
\begin{itemize}
\item[*] Developed an intelligent voice assistant web App, enabled users to order food, book tickets, navigate, etc, in an integrated platform. Built UI, frontend structure with \textbf{React}, \textbf{Redux}, and \textbf{Bootstrap}, designed dialogue processing flow to offer users prompt and accurate responses.
\item[*] Implemented navigation part. Applied Mapbox GL JS and related Plugins to support precheck for query, visualize realtime route information, intelligently offer route plan, etc.
\end{itemize}
\item[$\bullet$] \textbf{NLP Data Collection Platform}
\begin{itemize}
\item[*] Designed frontend page for an NLP Data Collection Platform. Enabled users to input sample sentences, apply different NLP models, and labeled for the processed result.
\item[*] Built Backend service for the platform. Received and processed \textbf{RESTful} request, applied \textbf{Apache Thrift} RPC framework to call NLU/NLP service, stored data and corresponding labels into \textbf{MongoDB} database. 
\end{itemize}
\end{itemize}

\cventry{11/2020--12/2020}{Yelp-like App Development}{Course Project}{}{}{}{}
\begin{itemize}
\item[*] Develop an application to realize basic functions of Yelp. Users are allowed to release and review a post on the homepage, make comments and score on other posts.\href{https://morning-sea-07913.herokuapp.com/}{\textcolor{blue}{Project Address}},\href{https://github.com/ChrisD12138/Yelpcamp}{\textcolor{blue}{Source Code}}.
\item[*] Utilized Sessions \&\& Cookies for user authentication, AJAX to upload webpages. Dealt with common security problems such as Mongo Injection and Cross Site Scripting. 
\item[*] Applied Bootstrap to design webpages, Express module of Node.js to support backend service, and MongoDB as database. The project was deployed with MongoDB Atlas and Heroku.
\end{itemize}

 \cventry{08/2020--11/2020}{Data Mining Intern (Netease ThunderFire)}{Internship}{Hangzhou, Zhejiang, China}{}{}{}
\begin{itemize}
\item[*] Collected and extracted game data with \textbf{Hadoop} and \textbf{MySQL}. Developed and maintained a Business Intelligence platform, visualized the analytic data with \textbf{Python Django} and \textbf{Vue}.
\item[*] Utilized machine learning methods to make predictions on game trends. Worked across Finance, Player Analysis and was responsible for strengthening the connection between game players and game producers.
\end{itemize}

\cventry{07/2019--09/2019}{University at Buffalo}{Research Assistant}{Buffalo, NY, USA}{AI Lab}{}
\begin{itemize}
\item[*] Improve the performance of a pervasive deep learning model Transformer on translation tasks by generating repulsive samples of the attention parameters, utilizing algorithms including Stein Variational Gradient Descent and Stochastic Particle Optimization.
\item[*] Achieved state-of-the-art results on translation tasks, outperformed the baseline model by $0.8$ BLEU value on small-scale the model and $0.9$ BLEU value on the base-scale model
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\cvitem{Programming Language}{\textsc{C}, \textsc{JAVA}, \textsc{Python}, \textsc{MySQL}, \textsc{HTML}, \textsc{CSS}, \textsc{JavaScript}.}
\cvitem{Frameworks \& Tools}{Node.js, React.js, BootStrap, Docker, Git.}

\end{document}